Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-26 answer-to-reviewers.tex

\smallskip

\emph{The other paper Reviewer 1 refers to is:}

\nocite{2016:walter-coolen}
\bibliographystyle{elsarticle-harv}
\bibliography{refs}
\smallskip

\emph{We cite this paper in our manuscript in Section~4,
clearly stating, in the last paragraph before Section~4.1,
that our manuscript and the cited paper share the same basic approach, namely
Weibull component models with conjugate inverse Gamma priors
combined with a survival signature approach to calculate the system remaining life distribution (RLD).
As mentioned there, however, the focus of these two works is entirely different.
The cited paper develops an approach to use \textbf{sets} of inverse Gamma priors,
to allow for a sophisticated modeling of uncertainties in the component models,
resulting in \textbf{sets} of RLDs which are the ultimate result of the paper.
Instead, the present manuscript uses the basic approach to develop a \textbf{maintenance policy},
using \textbf{a single} RLD as input for an optimization of the mean cost rate to find the cost-optimal moment of system maintenance.
Sections~4.1 to 4.3 describe the approach used for RLD calculation
in a similar way as in the cited paper,
but with notation adapted to the present manuscript's objective, i.e., defining a maintenance policy.
For readers to be able to understand our approach,
we considered it necessary to include a detailed description of the RLD calculation,
and not just refering to the paper.
}

@@

\medskip

I have the following questions that I hope the authors can answer.\\
Questions:
\begin{enumerate}
\item In cases of pessimistic and optimistic priors, should we continually update or do not update component reliability in terms of minimizing the overall cos[t]?

\smallskip

\emph{In both cases, it is optimal to continuously update the component model parameters.
This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
Section~6.2 covers the case of failures happening later than expected, i.e., a pessimistic prior is considered,
and the last paragraph before Section~6.3 (beginning with ``The effect of the continuous parameter update \ldots'')
gives a detailed explanation.
Section~6.3 studies a case with failure times earlier than expected, i.e., with a too optimistic prior.
Here, as described in the text, both the approach with and without continuous parameter update
trigger maintenance at the same time, leading to the same costs.
However, Figure~8 shows that without continuous parameter update, the system RLD is overestimated,
which may lead to an excess risk of system failure.
This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
than the approach without continuous parameter update (CBM-epu and CBM-npu).
Citing the last sentence of Section~7,
``[o]verall, it seems that CBM-cpu can exert its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.''
It is almost alway impossible to know beforehand if priors are too optimistic or too pessimistic.}

\item For the example system, I think we can simply use the key stone method (use H as the key stone) to calculate the system reliability when the components are independent.  Is it necessary to use system signature?

@@

\smallskip

\emph{The example system was deliberately chosen to be very simple,
and for such a system, indeed a simpler methodology like the keystone method can very well suffice.
However, our survival signature based method is also applicable to much larger systems with complex structures,
for which the keystone method is not practical.
We now emphasize this more explicitely,
and refer to a recent paper on survival signature computations for large and complex systems (Reed 2017).
Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the
survival signature from any given system graph,
thus avoiding manual computations as necessary in the keystone method.}
%no one component can be singled out as the reliability-limiting force.\\
%***add a note on simplicity (to understand what's going on) at example intro in Section~3?***}
\end{enumerate}

@@

The problem addressed is important and the methodology well-grounded. However, the manuscript requires some important work before it can be accepted.

The English writing is good. However, the paper needs to be reviewed as some sections lack a proper structure and the argument is hard to follow. In particular Section~5 must be completely rewritten.

\smallskip

\emph{Yes, we rewrote Section~5 according to the reviewer's suggestions,
as detailed below in relation to the reviewer's technical and general comments.}

@@

\subsection*{\emph{Technical comments}}

\begin{enumerate}
\item The notational choice does not seem to be the most appropriate. The use of $\tnow$ is confusing and makes the reading of the paper cumbersome. I will suggest to use something more direct, as $t_j$, where $j=1,\ldots$ represents the $j$th scheduled intervention. With that choice, the notation $\tau^{\tnow}_*$ can be simplified to $\tau^*_j$ without any loss of generality of information. Moreover, with this notational choice (or a similar one) the expression $t_j=j \delta$ becomes natural and. [sic!]

\smallskip

\emph{Our approach evaluates the RLD and $\tausnow$ not only at a regular grid,
but also at the exact times of component failures.
The reviewer's suggestion would thus have us describe the set of re-evaluation times as
$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \,\cup\, (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$.
We think this adds unnecessary complexity at the early parts of the manuscript,
and thus prefer to denote $\tnow$ as a generic evaluation point.}

@@

\item The claim in the first paragraph of Section 5 is a strong one and should be properly proved or, at least, a reference must be provided.

\smallskip

\emph{We were not sure which claim exactly the reviewer refered to, maybe to
``Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.''
In the rewrite of Section~5, this sentence was dropped.}
%(It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
%But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
%such the probability mass of the RLD is moving closer to $\tnow$,
%which leads to $\tausnow$ being closer to $\tnow$ as well.)***}

@@

\item In Section 5.1, the authors indicate that if, for a given time $\tnow$, $\tau_*^{\tnow}<\delta$, then a preventive maintenance is triggered. I wonder if it will not be better to wait until $\tau_*^{\tnow}$? Given that $\tau_*^{\tnow}$ is---by definition---the optimal intervention time, it seems that the best action is to intervene precisely at that time.

\smallskip

\emph{Our reasoning, now better explained in the Introduction and in the rewritten Section~5,
is that $\delta$ gives the shortest inter-evaluation time period that can be realized from a hardware point of view,
and preventive maintenance is initiated only when $\tausnow < \delta$.
Therefore, initiating maintenance at $\tnow$ or $\tnow + \tausnow$ is practically equivalent.}
%Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
%I could change the simulations to execute repair at time $\tnow + \tausnow$,
%but then one needs to check whether there is a component failure (and with it, a system failure)
%between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
%If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
%do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}

@@

\item It seems that the authors assume constant preventive and corrective maintenance costs. However, in practice one finds that maintenance costs are often state dependent. Is their model suitable for this? Is it robust to different cost structures? How will their results be affected?

\smallskip

\emph{Yes, we indeed assume constant cost parameters in our manuscript.
We now comment on this in the Conclusion, where we now briefly explain how our model could be extended to allow
for costs depending on time and on system state.
Such dependencies will lead to a more variable $\tausnow$.}

@@

\emph{Upon re-inspection of Table~1, we have found some errors that we have now corrected,
and would like to apologize for the confusion that these errors may have caused.
(We did all calculations with the correct survival signature though.)
We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.}
%{\scriptsize
%(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
%(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
%Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
%Also note here that there is software to calculate $\Phi$?***}

\item Five subsequent operation cycles seems to be a rather short simulation horizon. I will suggest the authors to extend their analysis to, at least, 20-25 cycles.

\smallskip

\emph{We agree that the simulation study in our submitted manuscript is rather small,
but we think it is still sufficiently large to give general impressions on the performance of our method
and to identify the factors contributing to its performance.}
%Time restrictions (the first author is no longer employed at TU Eindhoven)
%unfortunately prevented us from extending the simulation study.}

@@

\item Beside the didactical advantages of the small example, the authors should consider a more realistic framework for testing their model. Results should be provided for a larger scale simulation exercise.

\smallskip

\emph{We decided to use the simple example also in the simulation study to provide clear insights
that could get lost with a more complex example.
Generally, more complex systems are possible, only increasing computation times,
and we now comment on the scalability of our approach when introducing the running example in Section~3.}
\end{enumerate}

@@

\subsection*{General Comments}

\begin{enumerate}
\item The authors claim that no degradation signal is used for monitoring the system’s state. However, they mention that the status of the components can be monitored continuously. How can this be done? This question becomes more important when the authors mention that certain inspections (which reveal the status of the systems) can be conducted periodically. This seems to be in contradiction with the continuous monitoring mentioned above. Could the authors be so kind to clarify this?

\smallskip

\emph{We would like to apologize to Reviewer 2,
and agree that our manuscript was indeed very confusing in this point.
We completely rewrote the introduction and other relevant parts,
hopefully making more clear now that 
we do not use a \textbf{usual} domain-continuous degradation signal, like, e.g., vibration measurements.
Instead, we assume a time-continuous signal from the components of the system, telling us only whether they work or not.
We also previously denoted our frequent re-evaluation of the system RLD by ``inspections'',
which was indeed not adequate, and we have changed our wording and explanations.}

@@

\item The fourth paragraph in Section 1, starting with “In this paper…” must be rewritten. Their argument is not clear and it may seem contradictory; e.g. “no degradation signal for the system is available” and later “each component sends a binary signal”. At the end, it is not clear how information is collected.

\smallskip

\emph{Agreed, this is one of the paragraphs that we changed substantially as mentioned in the answer to the previous question,
and we hope that our argument is now more clear.}
%Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
%but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
%I would also do not call our approach ``inspection-based'', as we now do in that paragraph.

@@

\item The definition of an operational cycle in the first paragraph of page 3 seems to be in conflict with the one provided elsewhere in the manuscript, in particular page 11, Section 5.

\smallskip

\emph{We previously wrote on p.~3: ``where an operational cycle starts with a new system,
and ends after this system has been replaced by an as good as new system'',
and in Section~5 we wrote: ``An operational cycle begins with system start-up,
and ends when either preventive maintenance is carried out, or a failure of the system occurs,
with subsequent corrective maintenance.''
Since we assume that both preventive and corrective maintenance result in an (as good as) new system state,
we don't quite see the conflict here.
In our rewriting of the Introduction and Section~5,
we now make more clear that in our approach, maintenance means replacing the whole system,
indicating in Section~5.2 when this is a reasonable assumption.
Furthermore, in the Introduction, we now write
``An operational cycle spans the time between two consecutive system maintenance actions.
We assume that in both preventive and corrective maintenance, the entire system is replaced or brought to an as good as new state,
and thus optimize the unit cost rate calculated over the time since the last system replacement.''}

@@

\item I suggest the authors to define all the acronyms on their first use. For example, CBM is used throughout the text, but never defined; and RDL is used from page 2, but not defined until page 3 (in Section 2).

\smallskip

\emph{CBM was defined in the first line of Section~1, where we wrote ``CBM (condition-based maintenance)''.
We now write ``condition-based maintenance (CBM)'' instead.
We are sorry that we indeed defined RLD too late, and now define it at the first use on page~2.}

@@

\item The assumption of independence of the components, that appears for the first time in page 5, must be mentioned earlier in the paper.

\smallskip

\emph{Yes, we now mention this early in the Introduction, in a separate paragraph on page~2.}

@@

\emph{Section~4.1 introduces the Weibull component models
and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
explaining the Bayesian parameter update step for right-censored lifetimes.
We think that Section~4.1 is crucial to the understanding of our method,
especially for readers not familiar with Bayesian approaches.
As mentioned in our answer to Reviewer~1's main comment,
Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
in a form that is adapted to the purpose of the present manuscript.
We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}

\item I suggest to place Figure 2 somewhere after parameters $m$ and $\delta$ are defined and the maintenance policy is described in Section 5.1 (for example at the end of the section). Otherwise, it is hard to follow.

\smallskip

\emph{We had placed Figure~2 (depicting the flowchart for the policy, now Figure~3) directly before Section~5.1 which explains the policy.
We agree that it should appear during or after the detailed description of the policy to avoid confusion,
and now have placed it within Section~5.2.}

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 4

@@

In case of a trigger of type (1),
the currently used models for component failure times are updated
to account for the extra lifetime observed for the components.
This information is taken into account via right-censored observations
in a Bayesian parameter update step.
In case of a trigger of type (2),
where a component has failed but the system is still functioning,
in addition to the component models also the reliability block diagram of the system is updated.
Based on the above changes,
it is determined in both cases whether the system should be replaced now,
or that this decision should be postponed until the next planned evaluation moment,
accepting the risk of a system breakdown before.
To determine the latter,
we calculate the `optimal' next evaluation moment %moment for system replacement***
based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
where an operational cycle starts with a new system, and ends after this system has been replaced by a new system.

@@

We denote by $\tnow$ the moment in time that the system is observed,
measured from the moment the present operational cycle has started,
which coincides with starting to use a new system.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for $\tnow$, the adaptive and dynamic time span $\tausnow$
which gives the time from $\tnow$ until the next optimal moment to re-evaluate the system.
%Close to system startup, $\tausnow$ will be large;
%but as components in the system age and some indeed fail over time,
%$\tausnow$ will typically decrease.
A preventive maintenance action is initiated
when $\tnow + \tausnow$ would be earlier than the next planned evaluation time point.
We describe this dynamic and adaptive maintenance policy in more detail in Section~\ref{sec:operationalprocedure}.
%a flow chart for the policy is given in Figure~\ref{fig:procedure}.

The optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
%An operational cycle begins with system start-up,
%and ends when either preventive maintenance is carried out,
%or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is numerically determined in this situation.
%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
%and a small simulation study is presented in Section~\ref{sec:sim}.

@@

Replacement schemes that do not replace all components during maintenance
would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper.
Optimizing over replacement schemes is, in our view, a higly interesting topic that merits an investigation of its own.
We will return to this in the conclusion (Section~\ref{sec:outlook}).

@@

Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in the conclusion (Section~\ref{sec:outlook}).
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.

@@

Overall, it seems that CBM-cpu can play its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.
%This means that experts may confidently tend towards pessimistic specifications
%of the component mean time to failures $\yzk$.

>>>>

To calculate the system RLD, we use the survival signature,
which allows to deal with different types of components each having an individual failure time model
(see Section~\ref{sec:sysrel}).
Here we assume that components of different types fail independently,
and that failure times of components of the same type are independent given the model parameters.

@@

In case of a trigger of type (1),
the currently used models for component failure times are updated
to account for the extra lifetime observed for the components.
This information is taken into account via right-censored observations
in a Bayesian parameter update step.
In case of a trigger of type (2),
where a component has failed but the system is still functioning,
in addition to the component models also the reliability block diagram of the system is updated.
Based on the above changes,
it is determined in both cases whether the system should be replaced now,
or that this decision should be postponed until the next planned evaluation moment,
accepting the risk of a system breakdown before.
To determine the latter,
we calculate the `optimal' next evaluation moment %moment for system replacement***
based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle.
An operational cycle spans the time between two consecutive system maintenance actions.
We assume that in both preventive and corrective maintenance, the entire system is replaced or brought to an as good as new state,
and thus optimize the unit cost rate calculated over the time since the last system replacement.

@@

We denote by $\tnow$ the moment in time that the system is observed,
measured from the moment the present operational cycle has started,
which coincides with starting to use a new system.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for $\tnow$, the adaptive and dynamic time span $\tausnow$
which gives the time from $\tnow$ until the next optimal moment to re-evaluate the system.
%Close to system startup, $\tausnow$ will be large;
%but as components in the system age and some indeed fail over time,
%$\tausnow$ will typically decrease.
A preventive maintenance action is initiated
when $\tnow + \tausnow$ would be earlier than the next planned evaluation time point.
We describe this dynamic and adaptive maintenance policy in more detail in Section~\ref{sec:operationalprocedure}.
%a flow chart for the policy is given in Figure~\ref{fig:procedure}.
%
The optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
%An operational cycle begins with system start-up,
%and ends when either preventive maintenance is carried out,
%or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.
%
Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is numerically determined in this situation.
%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
%and a small simulation study is presented in Section~\ref{sec:sim}.

@@

Replacing not all components during maintenance
would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper.
Optimizing over replacement schemes is, in our view, a higly interesting topic that merits an investigation of its own.
We will return to this in the conclusion (Section~\ref{sec:outlook}).

@@

Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in the Conclusion (Section~\ref{sec:outlook}).
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.

@@

Overall, it seems that CBM-cpu can exert its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.
%This means that experts may confidently tend towards pessimistic specifications
%of the component mean time to failures $\yzk$.
